Supplemental Information B: Full Annotated Analysis and Reproducible Code

### 2021-10-22 Methods-and-Results.Rmd
AOT-Participants added

@@

\subsubsection{Participants}

>>>>

\faQuestionCircle\ Unsure about order of study one and two. Currently chronological. But could also be: (1) main model works in larger student sample, (2) works in economic migrant sample, (3) test full thing in medical sample.

@@

```{r workerSampleInfo, include=FALSE}

workerOccupation <- 
  dtWorker$clean %>%
  select(PID, starts_with("occupation")) %>%
  mutate_all(as_factor) %>% 
  mutate_all(as.character) %>%
  replace(is.na(.), "") %>%
  unite("occupation", -PID, sep = "/") %>%
  mutate(occupation = trimws(occupation, which = "both", whitespace = "[/]")) %>%
  distinct

workerSampleInfo <- 
  dtWorker$clean %>%
  group_by(PID) %>%
  summarise(
    dailiesN = n(), 
    age = age,
    gender = as_factor(Gender),
    edu = as_factor(education_level)
  ) %>%
  distinct

workerSampleInfo <- merge(workerSampleInfo, workerOccupation)
rm(workerOccupation)

table(workerSampleInfo$gender)
table(workerSampleInfo$edu)
table(workerSampleInfo$occupation)
```

\subsubsection{Participants} After receiving ethical approval from the University of Groningen, we recruited `r nrow(workerSampleInfo)` migrants using the local paid participant pool and specifically targeted non-Dutch migrants to participate in our study for a compensation of up to 34 Euros – each two Euros for pre- and post-questionnaire as well as 50 Eurocents for every experience sampling measure. Participants reported on their interactions for at least 30 days with two daily measures (capturing the morning and afternoon). With this design, we aimed at getting 50-60 measurements per participant (\textit{M} = `r format(round(mean(workerSampleInfo$dailiesN),2), nsmall=2)`, \textit{M} = `r format(round(sd(workerSampleInfo$dailiesN),2), nsmall=2)`). This is a common number of measurements found in experience sampling studies \citep[e.g., for a systematic review see][]{AanhetRot2012} and should offer sufficient power to model processes within and between participants. The sample consisted of relatively young, educated, and western migrants from the global north ($M_{age}$ = `r format(round(mean(workerSampleInfo$age),2), nsmall=2)`, $SD_{age}$ = `r format(round(sd(workerSampleInfo$age),2), nsmall=2)`, `r nrow(workerSampleInfo %>% filter(gender == "Female"))` women, `r nrow(workerSampleInfo %>% filter(occupation == "student"))` students). The sample accurately describes one of the largest groups of migrants in the region \citep[][]{GemeenteGroningen2015}.
